---
title: "Database_exchange"
author: "FG"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(tidyr)
library(REDCapR)
library(gtools)
library(ggplot2)
library(dplyr)
```

```{r}
uri="https://redcap.charite.de/cru/api/"
meks_token='6FD30683ACBA439FA03060E3DEC67881'
mb_token='F612C968DA7C512C99AF4147B1F757FE'
```

# download maternal pregnancy data from meks_ct (biosamples + physical assessment)
```{r}
meks_ct <- REDCapR:::redcap_read(
batch_size = 30L,
interbatch_delay = 0.5,
continue_on_error = FALSE,
redcap_uri = uri,
token = meks_token,
forms = (c("a_krperliche_untersuchung_blutentnahme", "a_krperliche_untersuchung_ctkids2health", "a_krperliche_untersuchung")),
fields = "maternal_id"
)$data %>%
  filter(maternal_id > 1399)
```

# download imminschutz data from meks_ct
```{r}
meks_ct.immun <- REDCapR:::redcap_read(
batch_size = 30L,
interbatch_delay = 0.5,
continue_on_error = FALSE,
redcap_uri = uri,
token = meks_token,
forms = ("j_immunschutz"),
fields = "maternal_id"
)$data %>%
  filter(maternal_id > 1399)
```

# download maternal pregnancy data from memobaby
```{r}
memobaby <- REDCapR:::redcap_read(
batch_size = 30L,
interbatch_delay = 0.5,
continue_on_error = FALSE,
redcap_uri = uri,
token = mb_token,
forms = (c("mutter_bioproben_und_ku", "mutter_blutentnahme", "blutentnahme_medikamente", "labor")),
fields = "maternal_id"
)$data %>%
  filter(maternal_id > 1399)
```

# immunschutz from meks_ct
```{r}
meks_ct.immun %>%
  filter(redcap_event_name == "t2a_arm_1")
```


```{r}
meks_ct.t2 <- meks_ct %>%
  filter(redcap_event_name == "t2a_arm_1") %>%
  select(c(maternal_id, redcap_event_name, 
           physicalexam_date, a_maternalweight, a_saliva, a_kids2hphysexam_date, 
           # a_kids2hphysexam_date wird für a_saliva_date verwendet
           a_stool, a_stool_date, a_physexam_note, 
           a_physicalexam_blood_date, a_last_hb_value, a_blooddraw_yn, a_time_blooddraw,
           a_bloodsamples_meks___1, a_bloodsamples_meks___2, a_bloodsamples_meks___3, a_bloodsamples_meks___4, a_bloodsamples_meks___5, a_bloodsamples_meks___0, 
           a_last_meal, a_bloodpressure, a_currentbreastfeeding, 
           a_phys_exam_infection_4weeks, a_phys_exam_infect_start, a_phys_exam_infect_end,
           a_phys_exam_medication, a_phys_exam_med_count))
```

# MB-instrument: mutter_bioproben_und_ku 
```{r}
meks2mb.bio_ku <- meks_ct.t2 %>%
  select(c(maternal_id, redcap_event_name, 
           physicalexam_date, 
           a_maternalweight, 
           a_saliva, 
           a_kids2hphysexam_date, # a_kids2hphysexam_date wird für a_saliva_date verwendet
           a_stool, 
           a_stool_date, 
           a_physexam_note
           )) %>%
  
  dplyr::rename(a_saliva_date = a_kids2hphysexam_date,
                physicalexam_blood_date = a_physicalexam_blood_date
                )
```

# MB-instrument: mutter_blutentnahme
```{r}
meks2mb.blood <- meks_ct.t2 %>%
    select(c(maternal_id, redcap_event_name,
           a_physicalexam_blood_date, 
           a_last_hb_value, 
           a_blooddraw_yn, 
           a_time_blooddraw,
           a_bloodsamples_meks___1, a_bloodsamples_meks___2, a_bloodsamples_meks___3, a_bloodsamples_meks___4, a_bloodsamples_meks___5, a_bloodsamples_meks___0, 
           a_last_meal, 
           a_bloodpressure, 
           a_currentbreastfeeding, 
           a_phys_exam_infection_4weeks, 
           a_phys_exam_infect_start, 
           a_phys_exam_infect_end,
           a_phys_exam_medication, 
           a_phys_exam_med_count
           )) %>%
  dplyr::rename(physicalexam_blood_date = a_physicalexam_blood_date,
                last_hb_value = a_last_hb_value,
                blooddraw_yn=a_blooddraw_yn,
                time_blooddraw=a_time_blooddraw,
                bloodsamples___1=a_bloodsamples_meks___1,
                bloodsamples___2=a_bloodsamples_meks___2,
                bloodsamples___3=a_bloodsamples_meks___3,
                bloodsamples___4=a_bloodsamples_meks___4,
                bloodsamples___5=a_bloodsamples_meks___5,
                bloodsamples___0=a_bloodsamples_meks___0,
                last_meal=a_last_meal,
                bloodpressure=a_bloodpressure,
                currentbreastfeeding=a_currentbreastfeeding,
                blood_infection_4weeks=a_phys_exam_infection_4weeks,
                blood_infect_start=a_phys_exam_infect_start,
                blood_infect_end=a_phys_exam_infect_end,
                blood_medication=a_phys_exam_medication,
                blood_med_count=a_phys_exam_med_count
                )
```


# meks_ct medication during pregnancy wird in memobaby anders codiert, darum hier separat 
```{r}
meks_ct.t2.meds <- meks_ct %>%
  filter(redcap_event_name == "t2a_arm_1") %>%
  select(c(maternal_id, redcap_event_name, 
           a_phys_exam_med1_name, a_phys_exam_med2_name, a_phys_exam_med3_name, a_phys_exam_med4_name,
           a_phys_exam_med1_dose, a_phys_exam_med2_dose, a_phys_exam_med3_dose, a_phys_exam_med4_dose,
           a_phys_exam_med1_type, a_phys_exam_med2_type, a_phys_exam_med3_type, a_phys_exam_med4_type))
  
```

# meks_ct hat maternal hight in T1 erhoben
```{r}
meks_ct.t1 <- meks_ct %>%
  filter(redcap_event_name == "t1a_arm_1") %>%
  select(c(maternal_id, redcap_event_name, a_maternalheight))
```



